%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
%\documentclass[]{nakulcv}

\documentclass[]{nakulcv}
% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Ashwini Karanth}
\address{3151 Broadway,68\linebreak New York, New York} 
\contacts{(646)8749161 \linebreak ak3793@columbia.edu}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Project Manager}{Department of Design \& Construction }{July2016}
				\begin{itemize}
					\item Part of the ‘Green Infrastructure’ Team that is responsible for managing and collecting Storm water runoff through green roofs, rain gardens and right of way Bioswales. 	
					\item Responsible for Maintaining a project management information system to provide data for the planning and control of project development in Queens. 
					\item Work inculdes establishing time frames and cost schedules, determining and coordinating project activities required between the client agencies, contractors, and departments responsible for project completion. 
				\end{itemize}
				\begin{cvsubsection}{Intern}{Sherwood Design Engineers}{Dec 2015}
				\begin{itemize}
					\item Worked on developing illustrations, research and analysis for a publication.  
					\item Publication Named ‘Water Infrastructure; Equitable Deployment of Resilient Systems” actively participates in helping define policies for the UN Habitat III
					\item Based on water resilience and issues in California and Bangalore. 
				\end{itemize}
			\end{cvsubsection}
			\begin{cvsubsection}{Architect, Head of West Zone}{Decathlon Sports India}{July 2014-April 2015}
				\begin{itemize}
					\item Responsible for design and coordination of working drawings for the departments of construction, real estate and facilities of all new stores in the west region of India. 
					\item Developed four climate responsive store prototypes for design of future stores across south Asia. 
				\end{itemize}
			\end{cvsubsection}
			\begin{cvsubsection}{Architect Associate}{Design Plus,Bangalore}{Jan 2014-May 2014}
			\begin{itemize}
				\item Worked as a designer on three residential and one education institution.
				\item Projects are located in Karnataka, Kerala and Andhra Pradesh.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Trainee Associate}{Arcop Associates, Bangalore}{Aug 2013 – Dec 2013}
			\begin{itemize}
				\item Worked on construction documents and designs with focus on residential projects by DLF, Rajapura My Town projects and TPL developers.
				\item Worked on the urban revitalization of a city center in Kerala, Thrissur.
			\end{itemize}	
		\end{cvsubsection}
		\end{cvsection}
	\begin{cvsection}{Education}
		\begin{cvsubsection}{New York}{Columbia University}{Fall 2015 -- Fall 2016}
			\begin{itemize}
				\item Masters of Science in Architecture and Urban Design 
				\item Teacher’s Assistant, Fall 2015 and Spring 2016
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Bangalore, KA}{M.S.Ramaiah I.T}{Fall 2010 -- May 2014}
			\begin{itemize}
				\item B.Arch, May 2014 GPA:3.74
				\item Student leader, Vice-Captain of college
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	\begin{cvsection}{Academic Projects}
		\begin{cvsubsection}{Urban Design}{}{}
			\begin{itemize}
				\item \textbf{Community greenhouses} (Bronx, NY). 
				\item \textbf{Tourism \& way finding} (Beacon, NY). 
				\item \textbf{Water resiliency \& sea level rise} (California).
				\item \textbf{Lake Pollution \& agriculture} (Bangalore, India).
				\item \textbf{Social Housing \& water pollution} (Rio, Brazil). 
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Architecture}{}{}
			\begin{itemize}
				\item \textbf{“A city inside a city”, thesis} (Bangalore,India).
				\item \textbf{Commercial-Hotel, Book store, IT Park} (India).
				\item \textbf{Institutional-Art Campus} (India).
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	\begin{cvsection}{Additional Experience and Awards}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Columbia Design Challenge | Jan 2016} Finalist for Design and prototyping of an ecological waste water system. In collaboration with environmental engineers. 
				\item \textbf{Urban Land Institute} Design proposal for downtown Atlanta, Georgia. In collaboration with planners, real estate majors and urban designers.
				\item \textbf{UN-Habitat Design For Kenya | March 2016} In collaboration with students from Kenya to Imagine a rural Urban interface in Machakos.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item AutoCAD; Adobe Photoshop; Adobe Illustrator; Adobe inDesign; Adobe after effects; Trimble sketch up; JavaScript; Microsoft Project;
				\item Microsoft Office suite; Autodesk Maya; Manual rendering; Primavera Enterprise; Arc GIS; Rhino; HTML; CSS; Python;
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
\end{document}
