%%T License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
%\documentclass[]{nakulcv}

\documentclass[]{nakulcv}
% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Akash Chugh}
\address{\#208,1255 E University Dr\linebreak Tempe,AZ 85281} 
\contacts{(480)930-7017 \linebreak akash.chugh@asu.edu} 

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Developer}{Larsen \& Toubro Infotech}{July 2014-July 2016}
		\begin{cvsubsection}{Project: B.E Malaysia}{}{}
				\begin{itemize}
					\item	Generated Interactive reports programmatically for the production planning team that helped visualize the existing capacity and plan for future production.
					\item Remodeled various data dictionary objects such as Tables, Views, Structures and set up Table maintenance that resulted in 3x faster access of data.
					\item Automated the data uploading process that saved 100+ man hours per month.
					\item Enhanced the standard SAP modules using enhancements thus saving end user’s time by more than 10\%.
				\end{itemize}
			\end{cvsubsection}
		\end{cvsubsection}
	\end{cvsection}
		\begin{cvsection}{Education}
		\begin{cvsubsection}{Tempe, AZ}{Arizona State University}{Fall 2016 -- Expected Fall 2018}
			\begin{itemize}
				\item Masters in Computer Software Engineering, \textbf{GPA:4.11}
				\item Graduate Coursework: Advanced Data Structures and Algorithms; Mobile Development;Semantic Web,Programming and Language Paradigms;Project \& Process Management(Data Analytics);Software Enterprise: Inception \& Elaboration.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Bangalore, KA}{Sir M Visvesvaraya Institute of Technology}{Fall 2010 -- Fall 2014}
			\begin{itemize}
			\item B.E. in Information Science, May 2014, \textbf{70\%}
				\item UG Coursework: Object Oriented Concepts;Database systems; DBMS;Data Structures and Algorithms; Operating Systems.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{BeNutritious} (2016). An android application that provides nutritious meal suggestions based on the user’s current food habit.Analyzes user data with various sources and predicts the best meal based on current day's nutrient deficiency.Additionally, Personal Software Process (Watts Humphrey) metrics were also evaluated during development for personal improvement and each development phase documented. \textbf{Java,SQLite,Android Studio} 
				\item \textbf{Sportsvaganza} (2016). A semantic web application that provides trending sports news based on the user’s country.Additionally, upcoming events,their wiki descriptions and tweets by sports icon are also displayed.Python was used to scrape data, and  to analyze raw data files.The application analyzes meta data associated with the news and generates RDF’s which are queried later. \textbf{Python,RDF,Turtle,SPARQL,JSP}
				\item \textbf{mAspira} (2017).A mobile application that is used by clinics and patients to monitor Asthma in children and remind them to carry out tests based on various sensors. The research work pertains to analyzing the aspect oriented concepts to achieve greater efficiency by optimizing logging, by making it target specific instead of using a brute force approach.\textbf{Java, Android Studio, Profiling Tools}
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	\begin{cvsection}{Additional Experience and Awards}
		\begin{cvsubsection}{}{}{}	\begin{itemize} \item \textbf{SAP Centre of Excellence Award:}Received the award from Johnson Controls Inc in recognition of my dedication and excellent work for delivering high quality objects.  \item \textbf{Partner's Award:}Contributed to Gyankosh(Larsen \& Toubro's library of reusable objects).  \item \textbf{Research/Travel grant reviewer-GPSA} (2016-17) Reviewing and approving grant applications from candidates in research.  \end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Python;Java;Swift;ABAP(SAP);HTML5;CSS3;Prolog.
				\item Android Studio;XCode;Eclipse;SAP;Vim;WebStorm; PyCharm; Linux.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
\end{document}
