%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
%\documentclass[]{nakulcv}

\documentclass[]{nakulcv}
% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Nakul Chawla}
\address{\#208,1255 E University Dr\linebreak Tempe,AZ 85281} 
\contacts{(480)930-6967 \linebreak nchawla3@asu.edu}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Skills Profile}
		\begin{cvsubsection}{Administration}{}{}
			\begin{itemize}
				\item Three Years of work experience in Target Corporation India as Developer Business Intelligence and Analytics.
				\item Efficient at multitasking
				\item Leadership skills, organizational skills and time management.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Communication Skills}{}{}
			\begin{itemize}
				\item Communication by phone, email and in person.
				\item Good communication skills that help in interacting internationally anywhere.
				\item Good interaction with all levels of management in the previous organization.
				\item Experience in presenting complex information to large groups. 
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Management}{}{}
			\begin{itemize}
				\item Experience in designing and implementing prototype for a project from scratch and then transferring the knowledge to the other teammates.
				\item Experience in client service management.
				\item Involved in creating and maintaining technical and procedural documentation.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Computer Skills}{}{}
			\begin{itemize}
				\item Proficient in full Microsoft office suite and good knowledge of excel sheets.
				\item Good experience of programming in C, C\#,python, javaScript, angularJs, SQL
				\item Good typing speed.
				\item Knowledge of conflict resolution tactics.
				\item Decision making skills.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	\begin{cvsection}{Academic Background}
		\begin{cvsubsection}{Tempe,AZ}{Arizona State University}{Fall 2016 -- Expected Fall 2018}
			\begin{itemize}
				\item	Master's in Computer Science  
				\item Graduate Coursework:Statistical MAchine Learning;Principles of programming languages;Distributed \& Multiprocessor OS
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Bangalore,KA}{MS Ramaiah IT}{Fail 2009 -- May 2013}
			\begin{itemize}
				\item B.E. in Information Science, May 2013 GPA:3.53
				\item UG Coursework: Databases;DBMS;Algorithms;Business Intelligence; Data Structures and Algorithms;
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	\begin{cvsection}{Related Experience}
		\begin{cvsubsection}{Bangalore,KA}{Target Corporation}{July 2013 -- July 2016}
			\begin{itemize}
				\item Handled internation clients calls concerning project design and functionality.
				\item Strong organizational and communication skills with the ability to concurrently direct multiple business activities.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	\begin{cvsection}{Strengths}
		\begin{cvsubsection}{}{}{}
		\begin{itemize}
			\item Leadership quality
			\item Disciplined and possess good communication skills
			\item Possess great problem-solving skills
		\end{itemize}
	\end{cvsubsection}
	\end{cvsection}
\end{document}
