%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Nakul}{Chawla}
\address{1255 E University Dr, Apt 208, Tempe, AZ 85281}
\mobile{(+1) 480-930-6967} 
%%% Social
\email{nchawla3@asu.edu}
\homepage{www.nakulchawla.com}
\github{nakulchawla09}
\linkedin{nakulchawla09}
%%% Optionals
\position{Graduate Student{\enskip\cdotp\enskip}at ASU}
\quote{"Never argue with data."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\recipient
%  {Company Recruitment Team}
%  {Google Inc.\\1600 Amphitheatre Parkway\\Mountain View, CA 94043}
%\letterdate{\today}
%\lettertitle{Job Application for Software Engineer}
%\letteropening{Dear Mr./Ms./Dr. LastName,}
%\letterclosing{Sincerely,}
%\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Nakul Chawla~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}
\cvparagraph{About Me}
I am currently a full-time student at Arizona State University (ASU) at Tempe, Arizona. I am scheduled to graduate in May 2018 with a degree in Master’s in Computer Science.
Previously, I was working with Target India Corporation at Bangalore as a Developer in Business Intelligence and Analytics for 3 years.
I have a 2-year experience in developing web applications at Target. I was responsible for developing full stack web applications.
My responsibility as a web developer ranged from designing/warehousing the database that would support the application, developing REST APIs and building responsive User-interfaces. The application I worked for the longest period
in my experience involved cleansing and normalizing data using complex SQL queries, warehousing and designing the database in SQL Server, the services and APIs in .Net/C\#, functionality in angularJs and the front end design in 
HTML5,CSS3, twitter-bootstrap. I have spent a large part of my time designing web pages for the clients, making them very responsive to all platforms and screen sizes. Most of the code was written in C\#, where I had segregated the 
layers in services, model(data and domain layer), and in order to utilize the objects properly, a shared DTO layer. The services utilized LINQ and entity framework and MVC 5.5.
The data warehousing included good amount of understanding in data models and normalization concept. I was able to normalize one big table of raw data in 27 normalized tables, and also was able to edit standards for modeling at 
Target to be able to match the new frameworks in application development.
I have 1 year of experience in big data analytics where I developed scripts in python to analyze Guest Shopping Patterns at Target. The project was to map each guest that shops at Target into a polygonal block whose latitude and 
longitude details are provided by the US Government. 
%The data that we were dealing here was transactional data of Target guests that accounted to 75 million records every day. We were sqooping this data on a daily basis and writing extensive SQL queries on hive to clean this data for 
%analysis in Spark. The analysis was mostly geo based analytics where we were trying to find the market area of a store using this data, so that we can improve upton the supply chain and shelf space at Target stores based on the 
%demographics of the store. 
At ASU, I worked on a machine learning problem, that had close to 160GB unclean data that was given by KDD Microsoft Graph API. I worked on cleaning and querying this data to prepare it for feature engineering models that we used later.

\cvparagraph{Why Me?}
I have worked extensively in web development where I developed and maintained loosely coupled multi-tier applications that required Object Oriented programming. I was responsible for managing the full stack along with the 
configuration and implementation on Windows Server microsoft cloud. I implemented repositories and database factory for database design patterns. For commit and rollback, I implemented unit of work pattern. As for dependency 
injection, I used Autofac.Since the data was in the most raw form, I had a handful of experience in cleansing, designing the completely de-normalized data that was at many different locations into one normalized ACID database and 
implementing it into production for the Real Estate Tax team at Target. 
Since I was a part of a Business Intelligence team in Finance and Marketing, the job required for me to write extensive SQL queries and work with big data on a regular basis. These queries included working on multiple systems and 
integrating them using APIs or services. 
I have worked in big data environment where I was required to send close to 75 million records daily from Teradata to Hive using SQOOP embedded SQL queries and then analyzing that guest data using python on pySpark.A lot of this work 
included working with geospatial data and analyzing guests based on those datasets. 
%Also, I am taking 2 courses this semester, the first one advances in databases where I will be working in building spatial index to make get faster retrievals of geo data on an in memory system, the second one distributed database 
systems where I will be working on geoSpqrk to analyze traffic hot spots in realtime in a city.
With respect to mapping my work to the agile teams goal, I have used JIRA integrated with hipchat and have experience using Github,MSTFS and other code versioning systems in order to maintain all versions of code.

\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
