%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
%\documentclass[]{nakulcv}

\documentclass[]{nakulcv}
% For mathematical symbols
\usepackage{amsmath}
\usepackage{url}

% Set applicant's personal data for header
\name{Nakul Chawla} \linebreak
\address{\#208,1255 E University Dr\linebreak Tempe,AZ 85281} 
\contacts{(480)930-6967 \linebreak \url{http://www.nakulchawla.com} \linebreak nakulchawla09@gmail.com}


\begin{document}

% Print the header
\makeheader

% Print the content
\begin{cvsection}{Skills}
	\begin{cvsubsection}{Programming Languages}{}{}	
		\begin{itemize}
			\item C\#; Python; C; C++; .Net;.Net core; scala;
		\end{itemize}
	\end{cvsubsection}
	\begin{cvsubsection}{Frameworks}{}{}
		\begin{itemize}
			\item node.js; angularJs; angular2; d3.js; JavaScript; jQuery; HTML5; CSS3 ; hadoop; spark;
		\end{itemize}
	\end{cvsubsection}
	\begin{cvsubsection}{Databases}{}{}
		\begin{itemize}
			\item PostgreSQL; Microsoft SQL Server; Teradata; firebase;
		\end{itemize}
	\end{cvsubsection}
	\begin{cvsubsection}{Misc}{}{}
		\begin{itemize}
			\item Git; JIRA; RESTful API WebServices; Jenkins; IIS;
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}
\begin{cvsection}{Employment}
	\begin{cvsubsection}{Software Application Developer}{Arizona State University}{March 2017 - Present}
		\begin{itemize}
			\item Working on a full stack application for administration of Doctorate students in College of Speech and Hearing.\textbf{.Net core, angularJs}
			\item Designing the application and integrating it with blackboard for a better user experience.
			\item Providing more administrative features to the department for better understanding the growth and development of the PhD students.
		\end{itemize}
	\end{cvsubsection}
	\begin{cvsubsection}{Business Intelligence Developer} {Target Corporation}{July 2015-July 2016}
		\begin{itemize}
			\item Implememted algorithms to find out the trade area for each store at Target.\textbf{hadoop, pyspark, python, sql, hive}
			\item Built and deployed scripts to automate the process for analysing the Guest shopping patterns at Target stores in California.
			\item Built scripts to realise ray casting algorithm in order to find locations of Target guests.\textbf{python}
			\item Analysed the demographics and merchandise correlation for target stores to optimise the supply chain expense.
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}

	\begin{cvsubsection}{Full Stack Developer}{Target Corporation}{July 2013-July 2016}
		\begin{itemize}
			\item Launched a full stack MVC Single Page application for real estate tax analysis saving about half a million dollars per year. \textbf{C\#,.Net, angularJs,sql server}
			\item Built and had complete ownership of the application to track the real estate tax for each store.
			\item Built and owned modules to support the court appeals for each store owned by Target.
			\item Built and owned a full stack application for managing Vendor Income documents and analysing collected income and profits out of the vendor income.\textbf{HTML5,jQuery, SQL}
			\item Built and deployed application for inventory shortage analysis and supply chain analysis for stores and target.com merchandise.\textbf{SQL, html5, javaScript}
			\item Implemented complete reporting for Real Estate Tax, Inventory Accounting and Analysis, Vendor Income for further analytics.
		\end{itemize}
	\end{cvsubsection}
\begin{cvsection}{Education}
	\begin{cvsubsection}{Tempe, AZ}{Arizona State University}{Fall 2016 -- Expected Fall 2018}
		\begin{itemize}
			\item Masters in Computer Science, GPA:3.33
			\item \textbf{Graduate Coursework} : Statistical Machine Learning; Principles of Programming Languages; Distributed Database Systems; Knowledge Representation \& Reasoning; Advance topics in Databases;
		\end{itemize}
	\end{cvsubsection}

	\begin{cvsubsection}{Bangalore, KA}{M.S.Ramaiah I.T}{Fall 2009 -- Summer 2013}
		\begin{itemize}
			\item B.E. in Information Science, Summer 2013 GPA:3.53
			\item \textbf{UG Coursework} : Database systems; DBMS; Business Intelligence; Data Structures and Algorithms; Object Oriented Programming;
		\end{itemize}
	\end{cvsubsection}

\end{cvsection}

\begin{cvsection}{Technical Experience}
	\begin{cvsubsection}{Projects}{}{}
		\begin{itemize}
			\item \textbf{KDD 2016 Paper Acceptance Rank Prediction} (2016). Predicting the ranking of an institution based on heterogeneous data provided by Microsoft Academic Graph API. Used Brown's Simple Exponential Smoothing, SVM Rank and Gradient Boosting Decision Trees to predict ranks and evaluating them using the Normalized Discounted Cumulative Gain.\textbf{Python,SQL, Google Big Query} 
			\item \textbf{Custom Compiler for python like language in ANSI C} (2016). Developed parser and compiler for a python like language in 5 stages entirely written in \textbf{C}.
			\item \textbf{Spatial indexing for an in-memory geospatial database} (2017). Implementing spatial indices for a geo-spatial in memory database.Potimising the implementation of PR-Quadtrees and PRM-Quadtrees to make indexes work in a cache conscious way. Critical analysis of research papers in in-memory database systems.\textbf{C++}
				%			\item \textbf{Distributed Database Systems} (2017). Setting up a 3 node hadoop cluster, and geo-spark for analyzing hot spots for cab drivers in a city. \textbf{Scala}
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}

\begin{cvsection}{Additional Experience and Awards}
	\begin{cvsubsection}{}{}{}	
		\begin{itemize}
			\item \textbf{Pyramid Award at Target:}for developing and automating Vendor Income Analysis faster than designated time period saving 100 hours of manual effort every month.
			\item \textbf{Partner's Award:}at Target for Vendor Income Analysis. 
			\item \textbf{Research/Travel grant reviewer-GPSA:} Reviewing and approving grant applications from candidates in research. 
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}
%\blfootnote{\url{https://www.nakulchawla.com} \\ \url{www.linkedin.com/in/nakulchawla09}}
\end{document}
